---
title: "A more complex example"
author: "Steph de Silva"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The basic example vignette took you through, well, the basics. But it wasn't particularly realistic, because if you already had all your data in R, you probably wouldn't need to be learning basic R. Most likely the data you need to work with right now is somewhere else.

This vignette will walk you through laoding an excel file and using some of the more advanced options in excelTransition to make the workflow easier to use.

Let's start from the beginning again and load the required packages. As we've already installed them, we can skip the `install.packages()` step. (And we don't need the `devtools` package this time as we're not installing a package from github.)

```{r, eval = FALSE, echo = TRUE}
library(readxl) # readxl is the package which allows you to load Excel files in R
library(ggplot2) # everybody likes charts, this is a great package to work with
library(openxlsx) # a package for writing excel files

library(excelTransition) # this is the package where the excelTransition functions live
```

So far so good, let's load our dataset. Let's try something a little more relevant to modern business than 14th century crop yields this time. To that end, we'll be using the loanbook from the Australian arm of [Ratesetter](www.ratesetter.com.au), which is a fintech company. Ratesetter specialises in marketplace lending: people can apply for a loan and other people can fund it. [They publish their loanbook every quarter](https://www.ratesetter.com.au/peer-to-peer-lending/statistics) and the loanbook we'll be using is from 30th September, 2017.

The spreadsheet is located in the data folder of the excelTransition package. You may need to change the path name to the data. The `sheet` argument tells R which sheet in the workbook it should read, while `col_names` tells R whether to look for column names to keep for each variable. The data doesn't start until row 9, so `skip = 8` tells R to skip all the irrelevant bits at the top.

```{r, eval = FALSE, echo = TRUE}
loanBook <- read_xlsx("../data/20170930loanbook.xlsx", sheet = "RSLoanBook",
                      col_names = TRUE, skip = 8)
            # Here, I'm loading the spreadsheet

```

In the basic example, the output from `makeDescriptives()` was just put in the current working directory. You generally want to choose where your output goes. I suggest making an output folder in your current directory. After that you can direct output - that's what the `outputName` argument is doing here. You may also want to choose the number of decimal places your descriptive statistics are rounded to. The default is `2` if you don't specify. Here `roundDP` specifies how much rounding. 

```{r, eval = FALSE, echo = TRUE}
outputName <- "output/descriptives.xlsx"
roundDP <- 3

myResults <- makeDescriptives(loanBook, roundDP, outputName) 
                # get the basic descriptives similar to Excel.

```

Likewise, you want to be able to put the charts somewhere you choose. There's an optional argument in `makeCharts()` to manage this too.
```{r, eval = FALSE, echo = TRUE}
pathName <- "output/"
makeCharts(loanBook, pathName)
```



